Attributes-based Object Classification and Segmentation

### 2010-05-12 paper.tex
paper updated

As object detection is generally only as good as the features used, so also it
appears that this approach to segmentation is only as good as the attribute
selection and training.  We found that in images with poor segmentations, the
confidences in prediction of car attributes were generally low.  One problem
with this implementation of attribute classifiers was that we didn't use
the selection criterion described in \cite{farhadi09} that enhances within
category prediction ability.  This means that, for example, the wheel attribute
is highly similar to the car attribute and thus its discrimative ability
is hurt.  One future direction for this research would be to improve the attribute
training using the additional selection criterion and observe effects on
the segmentations.

@@

>>>>

@@

As object classification is generally only as good as the features used, so also it
appears that this approach to segmentation is only as good as the attribute
selection and training.  We found that in images with poor segmentations, the
confidences in prediction of object-related attributes were generally low. The bounding 
boxes groundtruth can include many background features into the attribute models. Those 
features are very harmful. The extreme example is shown in the left image of figure \ref{fig:horse_bad_results}, 
which only segments out the background grass. However, even if we have the segmentation 
of objects as the groundtruth for training the attributes, we may still not have accurate 
models, since the groundtruth is for objects not for attributes. For example, if we train 
the attributes of wheel or metal only based on car images, we may get the car model not 
the attributes model. One way to deal with this problem is to directly label attributes 
groundtruth. Then we can get similar accurate attribute models as the object models.
